---
title: Homework 3
author: Luca Gisler
date: '`r Sys.Date()`' # You do not need to mess with this line
output: 
  html_document:
    number_sections: yes
    toc: yes
    toc_float: yes
---

Answer the following questions, along with Exercises 2.8.1-2, 6


**Question A:** Use the sign test to determine the following for the data set below:

- Find the 95% confidence interval for $\theta$ of the x2 data set.
- Find the sign test p-value for testing whether this data is coming from a distribution with mean of 0.
- Do we have evidence that this distribution is not coming from mean zero?

```{r}

set.seed(0)
x2 = runif(20)*4-1
alpha = 0.05
n <- length(x2)

s1 <- qbinom(alpha/2, n, prob = 0.5)
I = c(s1+1, n-s1)
sort(x2)[I]

sum(x2 > 0)

sum(2 * dbinom(16:20, 20, 0.5))

```

Null Hypothesis: Our true mean is 0
Alternative Hypothesis: true mean is not equal to 0

Our 95% Confidence Interval for estimate of $\theta$ is [0.5201407, 1.8704740]
since $\theta = 0$ is out of the range, we have evidence to reject the null.  The P-value is 0.01181793 that is < than 0.05 so we reject H0. 



**Question B:** Answer the same questions as Question A above using the t-test (using functions in R). 

```{r}
alpha = 0.05
n = length(x2)


t.test(x2, y = NULL , alternative = c("two.sided"), mu= 0, conf.level = 0.95)

```

Null Hypothesis: Our true mean is 0
Alternative Hypothesis: true mean is not equal to 0

Our 95% Confidence Interval for estimate of $\theta$ is [0.6975552, 1.7914825]
since $\theta = 0$ is out of the range, we have evidence to reject the null. 


**Question C:** How do the answers to the above 3 questions compare?

They both lead to the same result, although it is important to mention that the t-test operated more conservative in the way they defined the 95% Confidence Interval. It is interesting to see how they both rejected the null hypothesis but used different ways to get to that conclusion, the t-test generally assumes normal distribution and finds the p-value through the mean while the sign-test uses binomial distribution and finds the p-value through the median. 


# 2.8.1
Verify, via Simulation, the level of wilcox.test when sampling from a standard normal distribution. Use n = 30 and levels of alpha = 0.05. Based on the resulting estimate of alpha, the empirical level, obtain a 95 % confidence interval for alpha. 


```{r}
n = 30
nsims = 1000
alpha = 0.05

collwil = rep(0,nsims)

for(i in 1:nsims) {
  x = rnorm(n)
  wil =wilcox.test(x, mu = 0, conf.int = T)
  collwil[i] = wil$p.value
}

mean(collwil<0.05)

p_val = 0.1191



```


Hint: for the second part, say we found the empirical level for $\alpha = 0.01$ to be 0.102 over 1000 samples, the 95% CI for the empirical level for $\alpha = 0.01$ would be.

```{r}
p = 0.1191
n = 1000
SE = sqrt(p*(1-p)/1000)
SE

p + 1.96*SE
p - 1.96*SE
```

In 1000 simulations the Wilcoxon Test rejected around 11.91% the null hypothesis. The Standard Error for the Wilcoxon Test with n = 30 and mu = 0 is 0.01024281. The 95% confindence Interval for $\alpha = 0.01$ would be [0.1391759, 0.099042409]

# 2.8.2
levels: 0.1, 0.05, 0.01
df = 1,2,3,5,10

```{r}
set.seed(0)
n = 30
X = matrix( rt(n*10000, df = 1), ncol = n)

Wtest = function(x) wilcox.test(x)$p.value

pvals = apply(X,1,Wtest)
level = c( mean(pvals < 0.1),
           mean(pvals < 0.05),
           mean(pvals < 0.01) )
names(level) = paste('theta =', c(0.1,0.05,0.01))
level


library(knitr)
kable(level, caption = "Empirical Level of Theta")


```



# 2.8.6 

For Example 2.3.1 obtain a 90 % two-sided confidence interval for the treatement effect. 

```{r}

school <- c(82,69,73,43,58,56,76,65)
home <- c(63,42,74,37,51,43,80,62)
response <- school - home 

wilcox.test(response, alternative = "two.sided", conf.int = T,
            conf.level = 0.90)
t.test(response, alternative = "two.sided", conf.int = T, 
       conf.level = 0.90)

```

